Graph Learning from Binomial Signals'

### 2023-05-23 IEEE paper/GL_binary.tex
fix reference and front page

\title{Graph Learning from Binomial Signals'}

\author{Skip Moses, Jing Guo}
\thanks{This work was supported by the  Research, Scholarship, and Creative Activity (RSCA) Award from CSU, Chico. }
\thanks{Skip Moses is currently a graduate student in the College of Science and Mathematics, California Polytechnic University, San Luis Obispo, CA 93407 USA (e-mail: skipmoses@gmail.com).}
\thanks{The corresponding author Jing Guo is with the Department of Mathematics and Statistics, California State University, Chico, CA 95929 USA (e-mail: jguo2@csuchico.edu).}

@@

\bibliographystyle{IEEEtran}
\bibliography{rgl}

>>>>

\title{Graph Learning from Binomial Signals'}
\author{Skip Moses, Jing Guo
\thanks{This work was supported by the  Research, Scholarship, and Creative Activity (RSCA) Award from CSU, Chico. }
\thanks{Skip Moses is currently a graduate student in the College of Science and Mathematics, California Polytechnic University, San Luis Obispo, CA 93407 USA (e-mail: skipmoses@gmail.com).}
\thanks{The corresponding author Jing Guo is with the Department of Mathematics and Statistics, California State University, Chico, CA 95929 USA (e-mail: jguo2@csuchico.edu).}}

@@

\bibliographystyle{IEEEtran}
\bibliography{ref}
